% preamble %
\documentclass[12pt]{article}

% load preample %
\input{../../packages/preamble.tex}

% document %
\begin{document}

\title{%
    Scenarios\\
    \large Silhouette}
\date{}
\maketitle

\section{Scenarios}

\paragraph{Scenario 1}
Make two rulesets, one that is a regular ruleset and one that is a grid ruleset. Give each ruleset a unique selector. For the regular ruleset, add a blue background and change the text color to \#32a852. For the grid, define three columns and two rows of varied size. Lastly, apply both of the rulesets to a Container of type "header".

\paragraph{Scenario 2}
Make a table whose size changes dynamically, add values to the header row and add values to the rest of the rows as they are generated. Apply a class to the table and set a header color for the table.

\paragraph{Scenario 3}
Make a frontpage and two article pages and share a common stylesheet between them. Add a simple ruleset that targets the body element and give it a lightgreen background to see that the changes have applied to all the pages. Lastly, generate the code.

\paragraph{Scenario 4}
Make a simple form consisting of three input fields for username, password and submit. Label each of the fields accordingly and give the fieldset a legend of "Login Credentials".

\paragraph{Scenario 5}
Make a Container of type header and give it a navigation bar with links to all pages previously created. Make the navigation bar into a CSS flexbox so that all anchors be laid horizontally and justify the content to be "space-around".

\paragraph{Scenario 6}
Make a simple article page about yourself. Write your name in a level 2 heading at the top of the article, then add an unordered list containing containing key points about you. Lastly, add your email in bold text below the text.

\paragraph{Scenario 7}
Display a local video on your website and make sure that it supports at least three different file formats.

\paragraph{Scenario 8}
Make a questionnaire consisting of two questions. Make it so the first question has two possibilities and one correct answer, and so the second question has three possibilities with multiple correct answers. (Radio and Checkbox)

\paragraph{Scenario 9}
Remove underline for all anchors inside nav Containers and change the text color to red on mouse hover for each anchor.
    
\paragraph{Scenario 10}
Give the header a fixed gradient background from blue to red (right).

\paragraph{Scenario 11}
Define a grid that serves as a page layout, and give it three columns and one row with equally distributed length. Make sure to wrap them under each other once the screen is narrower than 1000px, such that there are one column and three rows.

\paragraph{Scenario 12}
Add an image to the frontpage with a source set containing 3 versions of the image (srcset) wrapped inside a 
figure-tag.

\paragraph{Scenario 13}
Add a video to the frontpage (using video-tag) consisting of 3 versions of the video and an error message.

\paragraph{Scenario 14}
Define a main grid for a website with 6 columns and 12 rows.

\paragraph{Scenario 15}
Make a keyframe animation for the footer to alternate between two colours.

\paragraph{Scenario 16}
Make a new HTML page. Set a custom title, and set the charset meta tag to "UTF-8".

\paragraph{Scenario 17}
Make a body element and append it to the HTML page. Then create header, main and footer elements and append it to the body element.

\paragraph{Scenario 18}
Give the header element a main heading for the page.

\paragraph{Scenario 19}
Make a second custom heading and add it to the main element. Make a paragraph element and give it an arbitrary Id.

\paragraph{Scenario 20}
Make a new rule set with the selector ".colors". When this rule set is applied, all elements marked with the corrosponding class should have a background color of blue, and a foreground color of magenta. Make sure to use the Property and Color enums for this.

\paragraph{Scenario 21}
Make a new rule set that should target all div elements. To this rule set, add a margin of 16 pixels and a padding of 2 em by using the Property and Unit enums.

\paragraph{Scenario 22}
Make a grid rule set with that affects all elements with an id of "mainGrid". For this grid, add two columns and three rows, and make it so the upper row is reserved for the header area, the middle row  is reserved for both main and aside areas, and the bottom row is reserved for the footer area.

\paragraph{Scenario 23}
Make an at-rule that changes the background color of the page to blue when the screen with is less than 1000 pixels.

\paragraph{Scenario 24}
Create a new stylesheet and give it a name and output location, then generate the stylesheet.

\end{document}